Plant-pollintor networks worldwide are composed by the same specific building

### 2021-05-30 Draft/Draft.Rmd
Update Draft.Rmd

We calculated the frequency of all motifs up to five nodes (see motif topologies in Figure 3 in [@simmons2019]) for each empirical network, by using the ‘bmotif’ package [@bmotifsimmons2019]. To control for variation in network size and for the fact that smaller motifs can be nested within larger motifs, motif frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains). Like [@simmons2020], we just used five-node motifs in our analyses for visualisation, interpretation and computational reasons. In addition, we also excluded two-node motifs (or links) from our analyses because their normalised frequencies would always equal one.

>>>>

We calculated the frequency of all motifs up to five nodes (see motif topologies in Figure 3 in [@simmons2019]) for each empirical network, by using the ‘bmotif’ package [@bmotifsimmons2019]. To control for variation in network size and for the fact that smaller motifs can be nested within larger motifs, the frequencies were normalised as a proportion of the total number of motifs within each motif class (i.e., the number of nodes a motif contains). Like [@simmons2020], we just used five-node motifs in our analyses for visualisation, interpretation and computational reasons. In addition, we also excluded two-node motifs (or links) from our analyses because their normalised frequencies would always equal one.
